KeysarMouseTracking.csv

### 2016-01-27 experiment2/analysis/exp2Analysis.Rmd
Incorporate turk judges into analysis; bootstrap errors

```{r}
messageCoding1 <- read.csv("../analysis/messageCoding1.csv")
messageCoding2 <- read.csv("../analysis/messageCoding2.csv")
relevantProperties <- c("gameid", "attemptNum", "condition", "critical",
                        "objectSet", "sender", "instructionNum")
overinformativeCodes <- messageCoding1 %>% 
  left_join(messageCoding2, by = relevantProperties) %>%
  filter(!(gameid %in% bannedIDsExp2)) %>%
  mutate(contents = contents.x, time = time.x) %>%
  select(gameid, attemptNum, condition, critical, objectSet, sender, 
         instructionNum, contents, time, targetCode1, distractCode1,
         altCode1, overCode1, targetCode2, distractCode2, altCode2,
         overCode2) %>%
  mutate(avgAltCode = (altCode1 + altCode2)/2,
         avgTargetCode = (targetCode1 + targetCode2)/2,
         avgDistractCode = (distractCode1 + distractCode2)/2,
         avgOverCode = (overCode1 + overCode2)/2)

# How often are the descriptions more informative than orig?
mean(overinformativeCodes$avgOverCode)

# How often do the descriptions apply to the hidden object?
mean(overinformativeCodes$avgDistractCode)

# Does overinformativity perfectly avoid picking distractor?
cor(overinformativeCodes$avgDistractCode, overinformativeCodes$avgOverCode)

# Inter-rater reliability
kappa2(cbind(overinformativeCodes$distractCode1, overinformativeCodes$distractCode2))
kappa2(cbind(overinformativeCodes$overCode1, overinformativeCodes$overCode2))
```

@@

```{r}
criticalErrors = errorDExp2 %>% 
  filter(attemptNum == 0)%>% 
  filter(criticalError == 1) 
itemWiseCodes <- overinformativeCodes %>% 
  left_join(criticalErrors, by = c("gameid", "condition", "critical", 
                                   "objectSet", "instructionNum",
                                   "attemptNum")) %>%
  select(gameid, objectSet, avgDistractCode, avgOverCode, 
         criticalError) %>%
  mutate(criticalError = ifelse(is.na(criticalError),0,1))

mmRes <- glmer(criticalError ~ avgOverCode + avgDistractCode +  (1 | objectSet),
      data = itemWiseCodes, family = binomial)

>>>>

```{r}
library(boot)
turkerRatings <- read.csv("../../normingExperiment/data/keysarNorming-trials.csv")
relevantProperties <- c("objectSet", "label")

criticalMessagesExp1 <- read.csv("../analysis/messagesExp1.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.1")
criticalMessagesExp2 <- read.csv("../analysis/messagesExp2.csv") %>%
  right_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.2")

overinformativeCodes <- rbind(criticalMessagesExp1, criticalMessagesExp2) %>%
  filter(!(gameid %in% bannedIDsExp2)) %>%
  filter(!(gameid %in% bannedIDsExp1))

summary(lmer(response ~ exp * referent + (1 | workerid) + (1 | objectSet), data = overinformativeCodes))

stat = function(data, indices) {
  d <- data[indices,]
  applicability = d %>%   
    group_by(exp, referent) %>%
    summarize(m = mean(response))
  print(applicability)
  return(applicability$m)
}

res = boot(data = overinformativeCodes, statistic = stat, R = 1000)
Exp1DistrCI = boot.ci(res, type = "basic", index=1)
Exp1targetCI = boot.ci(res, type = "basic", index=2)
Exp2DistrCI = boot.ci(res, type = "basic", index=3)
Exp2targetCI = boot.ci(res, type = "basic", index=4)

plottingDF = data.frame(referent = c("distractor", "target", "distractor", "target"),
                        exp = c("Exp.1", "Exp.1", "Exp.2", "Exp.2"),
                        response = res$t0,
                        lowerCI = c(Exp1DistrCI$basic[1,4], Exp1targetCI$basic[1,4],
                                    Exp2DistrCI$basic[1,4], Exp2targetCI$basic[1,4]),
                        upperCI = c(Exp1DistrCI$basic[1,5], Exp1targetCI$basic[1,5],
                                    Exp2DistrCI$basic[1,5], Exp2targetCI$basic[1,5]))
dodge <- position_dodge(width=0.9)
ggplot(plottingDF, aes(x = exp, y = response, fill = referent)) +
  geom_bar(stat = "identity", position = dodge) +
  geom_errorbar(aes(ymin = lowerCI, ymax = upperCI), position = dodge, width = 0.25) +
  theme_bw() +
  ylab("mean fitness of label")
ggsave("../../writing/cogsci-submission/images/fitnessInteraction.jpeg")

# spread out data, so each row is a label, and each column is a turker
wideRatings = turkerRatings %>% 
  group_by(workerid, label, referent) %>% 
  summarize(m = mean(response)) %>% 
  spread(workerid, m)

# Interrater reliability
icc(wideRatings[,-c(1,2)],
    model = "twoway", type = "agreement")

@@

```{r}
criticalErrorsExp1 = errorDExp1 %>%
  filter(attemptNum == 0) %>%
  filter(criticalError == 1) %>%
  mutate(exp = "Exp.1") %>%
  select(gameid, objectSet, exp, criticalError)
criticalErrorsExp2 = errorDExp2 %>% 
  filter(attemptNum == 0)%>% 
  filter(criticalError == 1) %>%
  mutate(exp = "Exp.2") %>%
  select(gameid, objectSet, exp, criticalError)

criticalErrors = rbind(criticalErrorsExp1, criticalErrorsExp2)

itemWiseCodes <- overinformativeCodes %>% 
  left_join(criticalErrors, by = c("gameid", "objectSet", "exp")) %>%
  mutate(criticalError = ifelse(is.na(criticalError),0,1))

mmRes <- glmer(criticalError ~ response * referent +  exp + (1 | objectSet),
      data = itemWiseCodes, family = binomial)
